Analysis of Prenatal Depression and Anxiety during Covid-19

### 2024-03-27 outputs/paper.qmd
modify the anxiety model based the modification of the anxiety variable

```{r}
#| label: fig-average_depression_and_anxiety
#| fig-cap: Distribution of Levels of Depression and Anxiety by Education and Household Income
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Levels of Depression by Education", "Distribution of Levels of Depression by Household Income", "Distribution of Levels of Anxiety by Education", "Distribution of Levels of Anxiety by Household Income"]
clean_data %>%
  group_by(maternal_education) %>%
  summarise(average_depression = mean(EPDS)) %>%
  ggplot(aes(x = maternal_education, y = average_depression)) +
  geom_bar(stat = "identity", fill = "cornflowerblue") + geom_text(aes(label = round(average_depression, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.7) +
  labs(x="Education", y="Average Level of Depression")

clean_data %>%
  group_by(household_income) %>%
  summarise(average_depression = mean(EPDS)) %>%
  ggplot(aes(x = household_income, y = average_depression)) + 
  geom_text(aes(label = round(average_depression, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.7)+
  geom_bar(stat = "identity", fill = "cornflowerblue") + labs(x="Household Income in 2019", y="Average Level of Depression")

clean_data %>%
  group_by(maternal_education) %>%
  summarise(average_anxiety = mean(PROMIS)) %>%
  ggplot(aes(x = maternal_education, y = average_anxiety)) +
  geom_bar(stat = "identity", fill = "salmon2") + geom_text(aes(label = round(average_anxiety, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.7)+
  labs(x="Education", y="Average Level of Anxiety")

clean_data %>%
  group_by(household_income) %>%
  summarise(average_anxiety = mean(PROMIS)) %>%
  ggplot(aes(x = household_income, y = average_anxiety)) + 
  geom_bar(stat = "identity", fill = "salmon2") +
  geom_text(aes(label = round(average_anxiety, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.7) +
  labs(x="Household Income in 2019", y="Average Level of Anxiety")
```

@@

clean_data |>
  ggplot(aes(x = threaten_life, y = PROMIS, color = language)) +
  geom_smooth(method = "lm") +
  theme_classic() + geom_hline(yintercept = 0.5, linetype = "dashed", color = "black")+
  geom_text(aes(x = 1, y = 0.5, label = "0.5"), color = "black", vjust = -0.5, hjust = 1) +
  labs(x="Perceived Level of Danger", y = "Level of Prenatal Anxiety")+ ylim(0,1)

clean_data |>
  ggplot(aes(x = threaten_baby_danger, y = PROMIS, color = language)) +
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  theme_classic() + 
  geom_text(aes(x = 1, y = 0.5, label = "0.5"), color = "black", vjust = -0.5, hjust = 1) +
  labs(x="Perceived Danger to Unborn Baby's Life", y = "Level of Prenatal Anxiety") + ylim(0,1) 
```

>>>>

```{r}
#| label: fig-average_depression_and_anxiety
#| fig-cap: Distribution of Levels of Depression and Anxiety by Education and Household Income
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Levels of Depression by Education", "Distribution of Levels of Depression by Household Income", "Distribution of Levels of Anxiety by Education", "Distribution of Levels of Anxiety by Household Income"]
clean_data %>%
  group_by(maternal_education) %>%
  summarise(average_depression = mean(EPDS)) %>%
  ggplot(aes(x = maternal_education, y = average_depression)) +
  geom_bar(stat = "identity", fill = "cornflowerblue") + geom_text(aes(label = round(average_depression, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.6) +
  labs(x="Education", y="Average Level of Depression")

clean_data %>%
  group_by(household_income) %>%
  summarise(average_depression = mean(EPDS)) %>%
  ggplot(aes(x = household_income, y = average_depression)) + 
  geom_text(aes(label = round(average_depression, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.6)+
  geom_bar(stat = "identity", fill = "cornflowerblue") + labs(x="Household Income in 2019", y="Average Level of Depression")

clean_data %>%
  group_by(maternal_education) %>%
  summarise(average_anxiety = mean(PROMIS)) %>%
  ggplot(aes(x = maternal_education, y = average_anxiety)) +
  geom_bar(stat = "identity", fill = "salmon2") + geom_text(aes(label = round(average_anxiety, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.6)+
  labs(x="Education", y="Average Level of Anxiety")

clean_data %>%
  group_by(household_income) %>%
  summarise(average_anxiety = mean(PROMIS)) %>%
  ggplot(aes(x = household_income, y = average_anxiety)) + 
  geom_bar(stat = "identity", fill = "salmon2") +
  geom_text(aes(label = round(average_anxiety, 3)), vjust = -0.5) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) + ylim(0, 0.6) +
  labs(x="Household Income in 2019", y="Average Level of Anxiety")
```

@@

clean_data |>
  ggplot(aes(x = threaten_life, y = PROMIS, color = language)) +
  geom_smooth(method = "lm") +
  theme_classic() + geom_hline(yintercept = 0.4, linetype = "dashed", color = "black")+
  geom_text(aes(x = 1, y = 0.4, label = "0.4"), color = "black", vjust = -0.5, hjust = 1) +
  labs(x="Perceived Level of Danger", y = "Level of Prenatal Anxiety")+ ylim(0,1)

clean_data |>
  ggplot(aes(x = threaten_baby_danger, y = PROMIS, color = language)) +
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0.4, linetype = "dashed", color = "black") +
  theme_classic() + 
  geom_text(aes(x = 1, y = 0.4, label = "0.4"), color = "black", vjust = -0.5, hjust = 1) +
  labs(x="Perceived Danger to Unborn Baby's Life", y = "Level of Prenatal Anxiety") + ylim(0,1) 
```
